Evaluating the Performance and Energy Efficiency of the COSMO-ART model system

### 2014-04-25 paper_enahpc14/Sec4:Experimental-results.tex
adds conclusion; modifies table

\begin{table}[htbf]
  \begin{center}
    \caption{Average power consumption (W) of the platforms}
    \label{tab:3}
    \begin{tabular}{ccc}
      \hline\noalign{\smallskip}
      \textbf{Simulation time} & \textbf{Xeon E5} & \textbf{Ivy Bridge EP} \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      \textbf{1 day} & 18122.01417 & 12658.52278 \\ 
      & 17979.61083 & 12586.40833 \\
      & 18065.45167 & - \\
      & 17973.02833 & - \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      \textbf{2 days} & 17997.57815 & - \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-0.eps}
  \caption{Time-to-solution and energy-to-solution comparison between
    Xeon E5 and Ivy Bridge-EP architectures}
  \label{fig:3}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-1.eps}
  \caption{Time-to-solution and energy-to-solution on
    \textsc{Tintorrum} - Polling mode}
  \label{fig:4}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-2.eps}
  \caption{Time-to-solution and energy-to-solution on
    \textsc{Tintorrum} - Polling mode}
  \label{fig:5}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-3.eps}
  \caption{Time-to-solution and Power on \textsc{Tintorrum} - Polling
    mode}
  \label{fig:6}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-4.eps}
  \caption{Time-to-solution and Power on \textsc{Tintorrum} - Blocking
    mode}
  \label{fig:7}
\end{figure}

\subsection{Power-performance tracing of COSMO-ART}
\label{subsec:4.3}

>>>>

\begin{table}[htbf]
  \begin{center}
    \caption{Average power consumption (W) of the platforms}
    \label{tab:3}
    \begin{tabular}{cccc}
      \hline\noalign{\smallskip}
      \textbf{\scriptsize{Xeon E5}} & \textbf{\scriptsize{Ivy Bridge}} & \textbf{\scriptsize{Xeon  E5645}} & \textbf{\scriptsize{Xeon  E5645}}\\
      & & \textbf{\scriptsize{(Polling)}} & \textbf{\scriptsize{(Blocking)}} \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      18035.0 & 12622.5 & 3713.6 & 3651.8 \\ 
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-0.eps}
  \caption{Time-to-solution and energy-to-solution comparison between
    Xeon E5 and Ivy Bridge-EP architectures for a 24h simulation}
  \label{fig:3}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-5.eps}
  \caption{Mean time-to-solution and energy-to-solution on
    \textsc{Tintorrum} for a 24h simulation - MPI Polling and Blocking
    modes}
  \label{fig:4}
\end{figure}

\subsection{Power-performance tracing of \textsc{Cosmo-art}}
\label{subsec:4.3}
